---
title: "WUP_04"
author: "Teresa Juan"
date: "June 2, 2022"
output:
  html_document:
    df_print: paged
---

```{r include=FALSE,echo=FALSE}
require(knitr)
require(tidyverse)
require(tigerstats)
GSScsv <- read.csv("GSScsv.csv") 

```

# Introduction

<!--In this section you explain what you are trying to show.  Where did the data come from?  What is the research or other question you are trying to answer?!-->

The data is in the file GSScsv.csv and came from the 2018 General Social Survey.  The question to answer is to resolve this hypothesis.  
$H_0$ There is no difference between the average score on the WORDSUM test and level of schooling DEGREE  
$H_a$ There is a significant difference in average score on the WORDSUM test between at least two levels of DEGREE  

# Methods

<!--Decide on your methods:  use "variable analysis" or other appropriate descriptors.  Make sure to choose at least one graphical method and at least one numerical method.!-->

# Results

<!--Divide this section into two sub-sections:  One for your descriptive  results and one for your inferential results.!-->

## Descriptive Results

### Graphical Descriptive Results

<!--Graphical results here.  Make sure to show your code.  Provide appropriate labels for axes, giving units if possible, and provide a good title for the graph, too.  Use the graphical results to describe the patterns if any that exist in the data as focused toward the research question!-->

```{r}
basicCN <- ggplot(GSScsv,aes(x=DEGREE,y=WORDSUM))

basicCN + geom_boxplot()
```

What we see in the box plot is that the LT HIGHT SCHOOL is below JUNIOR COLLEGE, GRADUATE, AND BACHELOR. But we also see that there is some similarities between LT HIGH SCHOOL and HIGHT SCHOOL DEGREE, If we would align them they wouldn’t bump in to each other. as we look at boxes we can see they are different. 

### Numerical Descriptive Results

<!--Numerical results go here. Use the numerical results to describe the patterns if any that exist in the data as focused toward the research question!-->

```{r}
favstats(WORDSUM~DEGREE,data=GSScsv)
```
As we make an observation on the data we can see that there is a difference in the mean of LT HIGHT SCHOOL and GRADUATE showing us that there more likely to be different as we run other test. We can also see that LT HIGH SCHOOL on Q3 is lower at 8.25 and GRADUATE its Q3 is at 11.00 quartile. meaning that those two boxes will not intersect with each other.

## Inferential Results

<!--State hypothesis clearly.  Make sure your discussion of the inferential test covers all the aspects that the test output produces, such as test statistic, p-value etc.  Make a decision about the null hypothesis, explain the assumptions on which the selected test/procedure was based, and why the chosen procedure satisfys the assumptions and is appropriate to answer the research question!-->

```{r}
model1 <- aov(WORDSUM~DEGREE,data=GSScsv)
summary.aov(model1)
```
The chances of see something like this, if there wasn't any difference between the means of all these five different subgroups is 2.36 out of 10,000. This test shows us there is a difference between these subgroups.

Now that we got our P valuw we want to find out wich category is actualy different from which category and to do this we are going to use the sequence of T-test using the TukeyHSD.

```{r}
#we specify the margins starting at the bottom and proceeding clockwise - thus 8.7 is the left side margin to hold the names of the factors
par(mar = c(3, 16.7, 2, 2))
plot(TukeyHSD(model1),las=2)
```

As we look at the interval of negative numbers on the left side we see that HIGHT SCHOOL GRADUATE and LT HIGHT SCHOOL GRADUATE don't cross over the line meaning these two sets are different from the other groups. we also see that the HIGHT SCHOOL GRADUATE AND LT HIGHT SCHOOL-JUNIOR COLLEGE almost meet at  intevals line so those two are a little different.

# Discussion and Conclusion

<!--Discussion and conclusion here.  If you found a relationship be sure to consider whether the relationship occurs because one of the variavbles causes the other, or whether they perhasps are related for some other reason.  Watch the chapter 6 videos from the GeorgeTown videos collection.!-->

In conclusion in order for us to find out if there is any difference between the level of schooling degrees we begin by doing our plot box. There we saw the WORDSOM that the LT HIGH SCHOOL and GRADUATE that if you alight them in the same line LT HIGHT SCHOOL would be completely underneath the GRADUATE, meaning there is a difference. Then we ran our date and we see that the MEAN of the GRADUATE is 10.09 and the LT HIGHT SCHOOL 7.75  are different. And as we did our P value we got a rely  small number 2.36, stating that in fact there is a difference but we needed to find out the difference between the other groups so we ran a tukeyHSD test. In order for us to find the difference between these tree groups we need to run the TukeyHSD test. The test showed us there is a difference between HIGHT SCHOOL and GRADUATES and LT LIGHT HIGHT SCHOOL by looking at the interval line they don't reach to 0 meaning everytime the interval line don't reach in fact there is a difference.
